---
title: "emorsa"
author: "YW"
date: "11/12/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(rwebppl)
library(here)
library(ggplot2)
library(tidyverse)
library(langcog)
library(patchwork)
library(ggpubr)
library(lme4)
library(brms)
rm(list = ls())
```
### Model a0: UttInfoEmoNon
```{r}
df <- expand.grid(
  utterance = c("good", "bad"),
  emotion = c("smile", "frown")
)

d.Ma0 <- webppl(
  program_file = here("models/Ma0_UttInfEmoNon.wppl"),
  data = df,
  data_var = "df"
)

d.Ma0.l1 <- bind_rows(d.Ma0$l1) %>%
  mutate(model = "Ma0:\nUttInfEmoNon")

# l1: state
Ma0.state <- d.Ma0.l1 %>%
  group_by(utterance, emotion, state, model) %>%
  summarize(expval = sum(prob)) 

# l1: infGoal
Ma0.infGoal <- d.Ma0.l1 %>%
  group_by(utterance, emotion, infGoal, model) %>%
  summarize(expval = sum(prob)) 

# l1: socGoal
Ma0.socGoal <- d.Ma0.l1 %>%
  group_by(utterance, emotion, socGoal, model) %>%
  summarize(expval = sum(prob)) 
```

### Model a1: UttInfEmoSoc
```{r}
df <- expand.grid(
  utterance = c("good", "bad"),
  emotion = c("smile", "frown")
)

d.Ma1 <- webppl(
  program_file = here("models/Ma1_UttInfEmoSoc.wppl"),
  data = df,
  data_var = "df"
)

d.Ma1.l1 <- bind_rows(d.Ma1$l1) %>%
  mutate(model = "Ma1:\nUttInfEmoSoc")

# l1: state
Ma1.state <- d.Ma1.l1 %>%
  group_by(utterance, emotion, state, model) %>%
  summarize(expval = sum(prob)) 

# l1: infGoal
Ma1.infGoal <- d.Ma1.l1 %>%
  group_by(utterance, emotion, infGoal, model) %>%
  summarize(expval = sum(prob)) 

# l1: socGoal
Ma1.socGoal <- d.Ma1.l1 %>%
  group_by(utterance, emotion, socGoal, model) %>%
  summarize(expval = sum(prob)) 
```
### Model a2: UttInfEmoBal
```{r}
df <- expand.grid(
  utterance = c("good", "bad"),
  emotion = c("smile", "frown")
)

d.Ma2 <- webppl(
  program_file = here("models/Ma2_UttInfEmoBal.wppl"),
  data = df,
  data_var = "df"
)

d.Ma2.l1 <- bind_rows(d.Ma2$l1) %>%
  mutate(model = "Ma2:\nUttInfEmoBal")

# l1: state
Ma2.state <- d.Ma2.l1 %>%
  group_by(utterance, emotion, state, model) %>%
  summarize(expval = sum(prob)) 

# l1: infGoal
Ma2.infGoal <- d.Ma2.l1 %>%
  group_by(utterance, emotion, infGoal, model) %>%
  summarize(expval = sum(prob)) 

# l1: socGoal
Ma2.socGoal <- d.Ma2.l1 %>%
  group_by(utterance, emotion, socGoal, model) %>%
  summarize(expval = sum(prob)) 
```

### Model a3: UttInfEmoSoc
```{r}
df <- expand.grid(
  utterance = c("good", "bad"),
  emotion = c("smile", "frown")
)

d.Ma3 <- webppl(
  program_file = here("models/Ma3_UttInfEmoTru.wppl"),
  data = df,
  data_var = "df"
)

d.Ma3.l1 <- bind_rows(d.Ma3$l1) %>%
  mutate(model = "Ma3:\nUttInfEmoTru")

# l1: state
Ma3.state <- d.Ma3.l1 %>%
  group_by(utterance, emotion, state, model) %>%
  summarize(expval = sum(prob)) 

# l1: infGoal
Ma3.infGoal <- d.Ma3.l1 %>%
  group_by(utterance, emotion, infGoal, model) %>%
  summarize(expval = sum(prob)) 

# l1: socGoal
Ma3.socGoal <- d.Ma3.l1 %>%
  group_by(utterance, emotion, socGoal, model) %>%
  summarize(expval = sum(prob)) 
```
### Model a4: UttInfEmoInf
```{r}
df <- expand.grid(
  utterance = c("good", "bad"),
  emotion = c("smile", "frown")
)

d.Ma4 <- webppl(
  program_file = here("models/Ma4_UttInfEmoInf.wppl"),
  data = df,
  data_var = "df"
)

d.Ma4.l1 <- bind_rows(d.Ma4$l1) %>%
  mutate(model = "Ma4:\nUttInfEmoInf")

# l1: state
Ma4.state <- d.Ma4.l1 %>%
  group_by(utterance, emotion, state, model) %>%
  summarize(expval = sum(prob)) 

# l1: infGoal
Ma4.infGoal <- d.Ma4.l1 %>%
  group_by(utterance, emotion, infGoal, model) %>%
  summarize(expval = sum(prob)) 

# l1: socGoal
Ma4.socGoal <- d.Ma4.l1 %>%
  group_by(utterance, emotion, socGoal, model) %>%
  summarize(expval = sum(prob)) 
```

### Model a5: UttInfoEmoTruInf
```{r}
df <- expand.grid(
  utterance = c("good", "bad"),
  emotion = c("smile", "frown")
)

d.Ma5 <- webppl(
  program_file = here("models/Ma5_UttInfEmoTruInf.wppl"),
  data = df,
  data_var = "df"
)

d.Ma5.l1 <- bind_rows(d.Ma5$l1) %>%
  mutate(model = "Ma5:\nUttInfEmoTruInf")

# l1: state
Ma5.state <- d.Ma5.l1 %>%
  group_by(utterance, emotion, state, model) %>%
  summarize(expval = sum(prob)) 

# l1: infGoal
Ma5.infGoal <- d.Ma5.l1 %>%
  group_by(utterance, emotion, infGoal, model) %>%
  summarize(expval = sum(prob)) 

# l1: socGoal
Ma5.socGoal <- d.Ma5.l1 %>%
  group_by(utterance, emotion, socGoal, model) %>%
  summarize(expval = sum(prob)) 

# l1: emoComm
Ma5.emoComm <- d.Ma5.l1 %>%
  group_by(utterance, emotion, emoComm, model) %>%
  summarize(expval = sum(prob))
```
### Model a6: UttInfoEmoTruSoc
```{r}
df <- expand.grid(
  utterance = c("good", "bad"),
  emotion = c("smile", "frown")
)

d.Ma6 <- webppl(
  program_file = here("models/Ma6_UttInfEmoTruSoc.wppl"),
  data = df,
  data_var = "df"
)

d.Ma6.l1 <- bind_rows(d.Ma6$l1) %>%
  mutate(model = "Ma6:\nUttInfEmoTruSoc")

# l1: state
Ma6.state <- d.Ma6.l1 %>%
  group_by(utterance, emotion, state, model) %>%
  summarize(expval = sum(prob)) 

# l1: infGoal
Ma6.infGoal <- d.Ma6.l1 %>%
  group_by(utterance, emotion, infGoal, model) %>%
  summarize(expval = sum(prob)) 

# l1: socGoal
Ma6.socGoal <- d.Ma6.l1 %>%
  group_by(utterance, emotion, socGoal, model) %>%
  summarize(expval = sum(prob)) 

# l1: emoComm
Ma6.emoComm <- d.Ma6.l1 %>%
  group_by(utterance, emotion, emoComm, model) %>%
  summarize(expval = sum(prob))
```
### Model a7: UttInfoEmoTruBal
```{r}
df <- expand.grid(
  utterance = c("good", "bad"),
  emotion = c("smile", "frown")
)

d.Ma7 <- webppl(
  program_file = here("models/Ma7_UttInfEmoTruBal.wppl"),
  data = df,
  data_var = "df"
)

d.Ma7.l1 <- bind_rows(d.Ma7$l1) %>%
  mutate(model = "Ma7:\nUttInfEmoTruBal")

# l1: state
Ma7.state <- d.Ma7.l1 %>%
  group_by(utterance, emotion, state, model) %>%
  summarize(expval = sum(prob)) 

# l1: infGoal
Ma7.infGoal <- d.Ma7.l1 %>%
  group_by(utterance, emotion, infGoal, model) %>%
  summarize(expval = sum(prob)) 

# l1: socGoal
Ma7.socGoal <- d.Ma7.l1 %>%
  group_by(utterance, emotion, socGoal, model) %>%
  summarize(expval = sum(prob)) 

# l1: emoComm
Ma7.emoComm <- d.Ma7.l1 %>%
  group_by(utterance, emotion, emoComm, model) %>%
  summarize(expval = sum(prob))
```


### Model b0: UttBalEmoNon
```{r}
df <- expand.grid(
  utterance = c("good", "bad"),
  emotion = c("smile", "frown")
)

d.Mb0 <- webppl(
  program_file = here("models/Mb0_UttBalEmoNon.wppl"),
  data = df,
  data_var = "df"
)

d.Mb0.l1 <- bind_rows(d.Mb0$l1) %>%
  mutate(model = "Mb0:\nUttBalEmoNon")

# l1: state
Mb0.state <- d.Mb0.l1 %>%
  group_by(utterance, emotion, state, model) %>%
  summarize(expval = sum(prob)) 

# l1: infGoal
Mb0.infGoal <- d.Mb0.l1 %>%
  group_by(utterance, emotion, infGoal, model) %>%
  summarize(expval = sum(prob)) 

# l1: socGoal
Mb0.socGoal <- d.Mb0.l1 %>%
  group_by(utterance, emotion, socGoal, model) %>%
  summarize(expval = sum(prob)) 
```

### Model b1: UttBalEmoSoc
```{r}
df <- expand.grid(
  utterance = c("good", "bad"),
  emotion = c("smile", "frown")
)

d.Mb1 <- webppl(
  program_file = here("models/Mb1_UttBalEmoSoc.wppl"),
  data = df,
  data_var = "df"
)

d.Mb1.l1 <- bind_rows(d.Mb1$l1) %>%
  mutate(model = "Mb1:\nUttBalEmoSoc")

# l1: state
Mb1.state <- d.Mb1.l1 %>%
  group_by(utterance, emotion, state, model) %>%
  summarize(expval = sum(prob)) 

# l1: infGoal
Mb1.infGoal <- d.Mb1.l1 %>%
  group_by(utterance, emotion, infGoal, model) %>%
  summarize(expval = sum(prob)) 

# l1: socGoal
Mb1.socGoal <- d.Mb1.l1 %>%
  group_by(utterance, emotion, socGoal, model) %>%
  summarize(expval = sum(prob)) 
```

### Model b2: UttBalEmoBal
```{r}
df <- expand.grid(
  utterance = c("good", "bad"),
  emotion = c("smile", "frown")
)

d.Mb2 <- webppl(
  program_file = here("models/Mb2_UttBalEmoBal.wppl"),
  data = df,
  data_var = "df"
)

d.Mb2.l1 <- bind_rows(d.Mb2$l1) %>%
  mutate(model = "Mb2:\nUttBalEmoBal")

# l1: state
Mb2.state <- d.Mb2.l1 %>%
  group_by(utterance, emotion, state, model) %>%
  summarize(expval = sum(prob)) 

# l1: infGoal
Mb2.infGoal <- d.Mb2.l1 %>%
  group_by(utterance, emotion, infGoal, model) %>%
  summarize(expval = sum(prob)) 

# l1: socGoal
Mb2.socGoal <- d.Mb2.l1 %>%
  group_by(utterance, emotion, socGoal, model) %>%
  summarize(expval = sum(prob)) 
```
### Model b3: UttBalEmoTru
```{r}
d.Mb3 <- webppl(
  program_file = here("models/Mb3_UttBalEmoTru.wppl"),
  data = df,
  data_var = "df"
  )

d.Mb3.l1 <- bind_rows(d.Mb3$l1) %>%
  mutate(model = "Mb3:\nUttBalEmoTru")

# l1: state
Mb3.state <- d.Mb3.l1 %>%
  group_by(utterance, emotion, state, model) %>%
  summarize(expval = sum(prob)) 

# l1: infGoal
Mb3.infGoal <- d.Mb3.l1 %>%
  group_by(utterance, emotion, infGoal, model) %>%
  summarize(expval = sum(prob)) 

# l1: socGoal
Mb3.socGoal <- d.Mb3.l1 %>%
  group_by(utterance, emotion, socGoal, model) %>%
  summarize(expval = sum(prob)) 
```

### Model b4: UttBalEmoInf
```{r}
d.Mb4 <- webppl(
  program_file = here("models/Mb4_UttBalEmoInf.wppl"),
  data = df,
  data_var = "df"
  )

d.Mb4.l1 <- bind_rows(d.Mb4$l1) %>%
  mutate(model = "Mb4:\nUttBalEmoInf")

# l1: state
Mb4.state <- d.Mb4.l1 %>%
  group_by(utterance, emotion, state, model) %>%
  summarize(expval = sum(prob)) 

# l1: infGoal
Mb4.infGoal <- d.Mb4.l1 %>%
  group_by(utterance, emotion, infGoal, model) %>%
  summarize(expval = sum(prob)) 

# l1: socGoal
Mb4.socGoal <- d.Mb4.l1 %>%
  group_by(utterance, emotion, socGoal, model) %>%
  summarize(expval = sum(prob)) 
```

### Model b5: UttBalEmoTruInf

```{r}
df <- expand.grid(
  utterance = c("good", "bad"),
  emotion = c("smile", "frown")
)

d.Mb5 <- webppl(
  program_file = here("models/Mb5_UttBalEmoTruInf.wppl"),
  data = df,
  data_var = "df"
  )

d.Mb5.l1 <- bind_rows(d.Mb5$l1) %>%
  mutate(model = "Mb5:\nUttBalEmoTruInf")

# l1: state
Mb5.state <- d.Mb5.l1 %>%
  group_by(utterance, emotion, state, model) %>%
  summarize(expval = sum(prob)) 

# l1: emoComm
Mb5.emoComm <- d.Mb5.l1 %>%
  group_by(utterance, emotion, emoComm, model) %>%
  summarize(expval = sum(prob)) 

# l1: infGoal
Mb5.infGoal <- d.Mb5.l1 %>%
  group_by(utterance, emotion, infGoal, model) %>%
  summarize(expval = sum(prob)) 

# l1: socGoal
Mb5.socGoal <- d.Mb5.l1 %>%
  group_by(utterance, emotion, socGoal, model) %>%
  summarize(expval = sum(prob)) 
```

### Model b6: UttBalEmoTruSoc

```{r}
d.Mb6 <- webppl(
  program_file = here("models/Mb6_UttBalEmoTruSoc.wppl"),
  data = df,
  data_var = "df"
  )

d.Mb6.l1 <- bind_rows(d.Mb6$l1) %>%
  mutate(model = "Mb6:\nUttBalEmoTruSoc")

# l1: state
Mb6.state <- d.Mb6.l1 %>%
  group_by(utterance, emotion, state, model) %>%
  summarize(expval = sum(prob)) 

# l1: emoComm
Mb6.emoComm <- d.Mb6.l1 %>%
  group_by(utterance, emotion, emoComm, model) %>%
  summarize(expval = sum(prob)) 

# l1: infGoal
Mb6.infGoal <- d.Mb6.l1 %>%
  group_by(utterance, emotion, infGoal, model) %>%
  summarize(expval = sum(prob)) 

# l1: socGoal
Mb6.socGoal <- d.Mb6.l1 %>%
  group_by(utterance, emotion, socGoal, model) %>%
  summarize(expval = sum(prob)) 
```

### Model b7: UttBalEmoTruBal

```{r}
d.Mb7 <- webppl(
  program_file = here("models/Mb7_UttBalEmoTruBal.wppl"),
  data = df,
  data_var = "df"
  )

d.Mb7.l1 <- bind_rows(d.Mb7$l1) %>%
  mutate(model = "Mb7:\nUttBalEmoTruBal")

# l1: state
Mb7.state <- d.Mb7.l1 %>%
  group_by(utterance, emotion, state, model) %>%
  summarize(expval = sum(prob)) 

# l1: emoComm
Mb7.emoComm <- d.Mb7.l1 %>%
  group_by(utterance, emotion, emoComm, model) %>%
  summarize(expval = sum(prob)) 

# l1: infGoal
Mb7.infGoal <- d.Mb7.l1 %>%
  group_by(utterance, emotion, infGoal, model) %>%
  summarize(expval = sum(prob)) 

# l1: socGoal
Mb7.socGoal <- d.Mb7.l1 %>%
  group_by(utterance, emotion, socGoal, model) %>%
  summarize(expval = sum(prob)) 
```

## line plots - graded
### state: models
```{r}
state0 <- rbind(Ma0.state, Ma1.state, Ma2.state, Ma3.state, Ma4.state, Ma5.state, Ma6.state, Ma7.state,
                Mb0.state, Mb1.state, Mb2.state, Mb3.state, Mb4.state, Mb5.state, Mb6.state, Mb7.state)
state <- state0 %>%
  mutate(condition = paste(utterance, emotion),
         condition = factor(condition, levels = c("good smile", "bad frown", "good frown", "bad smile")))
  
pd <- position_dodge(0.2)
state.plot <- ggplot(state, aes(x = state, y = expval, 
                                group = condition,
                                color=condition)) +
  geom_line(position=pd) +
  geom_point(position=pd) +
  scale_color_brewer(palette="Dark2") +
  theme_bw() +
  ylim(0, 1) +
  xlab("true state")+
  ylab("posterior probability mass") +
  theme(legend.position='none')+
  ggtitle("Model Predictions") +
  theme(legend.position='none',
        plot.title = element_text(hjust = 0.5)) +
  facet_grid(cols = vars(model))
state.plot
```
### state: human
```{r}
d.raw <- read.csv(here("models/201221EMO-RSA_MAIN_STATE_January 13, 2021_15.51.csv"))
d <- d.raw %>%
  slice(-1:-2) %>%
  filter(Consent != "") %>%
  select(ResponseId, starts_with("PUtt_"), starts_with("NUtt_")) %>%
  pivot_longer(cols = c(starts_with("PUtt_"), starts_with("NUtt_")), 
               names_to = "trial", values_to = "response") %>%
  separate(trial, into=c("utt","exp","race", "gender","question", "random")) %>%
  rename(id = `ResponseId`) %>%
  mutate(question = case_when(question == "GT" ~ "true state",
                              question == "check" ~ "check"),
         condition = case_when(utt == "PUtt" & exp == "PExp" ~ "PU_PE",
                               utt == "PUtt" & exp == "NExp" ~ "PU_NE",
                               utt == "NUtt" & exp == "PExp" ~ "NU_PE",
                               utt == "NUtt" & exp == "NExp" ~ "NU_NE"),
         condition = fct_relevel(condition, "PU_PE", "PU_NE", "NU_PE", "NU_NE"),
         response = fct_relevel(response, "1", "2", "3", "4", "5", "6")) %>%
  select(-random) %>%
  filter(response != "") 

checks <- d %>%
  filter(question == "check") %>%
  mutate(check_score = case_when(race == "A" & grepl("H", response, ignore.case = TRUE) ~ 1,
                                 race == "B" & grepl("O", response, ignore.case = TRUE) ~ 1,
                                 race == "L" & grepl("U", response, ignore.case = TRUE) ~ 1,
                                 race == "W" & grepl("L", response, ignore.case = TRUE) ~ 1,
                                 TRUE ~ 0)) %>%
  group_by(id) %>%
  summarize(perc_correct = mean(check_score))

ggplot(checks, aes(perc_correct)) +
  geom_histogram(binwidth=.01) +
  theme_bw() +
  xlab("accuracy on check questions") +
  ylab("number of participants")

# Only include those who got all check questions correct
d <- full_join(d, checks) %>%
  filter(perc_correct == 1) %>%
  filter

d2 <- d %>%
  mutate(utt = case_when(utt == "PUtt" ~ "good",
                         utt == "NUtt" ~ "bad"),
         exp = case_when(exp == "PExp" ~ "smile",
                         exp == "NExp" ~ "frown"),
         utt = fct_relevel(utt, "good"),
         exp = fct_relevel(exp, "smile"),
         condition = case_when(condition=="PU_PE" ~ "good smile",
                               condition=="NU_NE" ~ "bad frown",
                               condition=="PU_NE" ~ "good frown",
                               condition=="NU_PE" ~ "bad smile"),
         condition = factor(condition, levels=c("good smile", "bad frown", "good frown", "bad smile"))) %>%
  filter(question=="true state") %>%
  select(-perc_correct)

#write.csv(d2, here("models/clean_data_true_state.csv"), row.names = FALSE)

condition <- c('good smile', 'bad frown', 'good frown','good frown')
response <- as.factor(c(1, 5, 5, 6))
n <- c(0, 0, 0, 0)
zeros <- data.frame(condition, response, n)

n_condition <- d2 %>%
  group_by(condition) %>%
  count() 
n_condition

d.state <- d2 %>%
  group_by(condition, response) %>%
  count() %>%
  bind_rows(zeros) %>%
  mutate(proportion = case_when(condition=="good smile" ~ n/55,
                           condition=="good frown" ~ n/55,
                           condition=="bad smile" ~ n/55,
                           condition=="bad frown" ~ n/55),
         ci_l = case_when(condition=="good smile" ~ prop.test(n, 55)$conf.int[1],
                           condition=="good frown" ~ prop.test(n, 55)$conf.int[1],
                           condition=="bad smile" ~ prop.test(n, 55)$conf.int[1],
                           condition=="bad frown" ~ prop.test(n, 55)$conf.int[1]),
         ci_u = case_when(condition=="good smile" ~ prop.test(n, 55)$conf.int[2],
                           condition=="good frown" ~ prop.test(n, 55)$conf.int[2],
                           condition=="bad smile" ~ prop.test(n, 55)$conf.int[2],
                           condition=="bad frown" ~ prop.test(n, 55)$conf.int[2]))  

h.state.plot <- d.state %>%
  ggplot(., aes(x = response, y = proportion, group = condition, color=condition))+
  geom_line(position=pd) +
  geom_point(position=pd) +
  geom_pointrange(aes(ymin=ci_l, ymax=ci_u), size = 0.25, position=pd) +
  scale_color_brewer(palette="Dark2") +
  ylim(0, 1) +
  xlab("true state") +
  ylab("proportion chosen") +
  theme_bw() + 
  ggtitle("Human Data") +
  theme(plot.title = element_text(hjust = 0.5))
h.state.plot
```
### state: total
```{r}
state.total <- state.plot + h.state.plot + plot_layout(ncol=2, widths=c(16,1))
state.total
```
### infGoal: models
```{r}
# models
infGoal0 <- rbind(Ma0.infGoal, Ma1.infGoal, Ma2.infGoal, Ma3.infGoal, Ma4.infGoal, Ma5.infGoal, Ma6.infGoal, Ma7.infGoal, 
                  Mb0.infGoal, Mb1.infGoal, Mb2.infGoal, Mb3.infGoal, Mb4.infGoal, Mb5.infGoal, Mb6.infGoal, Mb7.infGoal)
infGoal <- infGoal0 %>%
  mutate(condition = paste(utterance, emotion),
         condition = factor(condition, levels = c("good smile", "bad frown", "good frown", "bad smile")))
  
pd <- position_dodge(0.2)
infGoal.plot <- ggplot(infGoal, aes(x = infGoal, y = expval, 
                                group = condition,
                                color=condition)) +
  geom_line(position=pd) +
  geom_point(position=pd) +
  scale_color_brewer(palette="Dark2") +
  theme_bw() +
  theme(legend.position='none')+
  ylim(0, 0.3) +
  #xlab("informational goal") +
  scale_x_continuous(name="informational goal", breaks = c(0, 0.4, 0.8)) +
  ylab("posterior probability mass") +
  #ggtitle("\"How likely do you think the speaker's goal was to provide accurate feedback?\"") +
  theme(legend.position='none',
        plot.title = element_text(hjust = 0.5)) +
  facet_grid(cols = vars(model))
infGoal.plot
```

### socGoal: models
```{r}
# models
socGoal0 <- rbind(Ma0.socGoal, Ma1.socGoal, Ma2.socGoal, Ma3.socGoal, Ma4.socGoal, Ma5.socGoal, Ma6.socGoal,Ma7.socGoal, 
                  Mb0.socGoal, Mb1.socGoal, Mb2.socGoal, Mb3.socGoal, Mb4.socGoal, Mb5.socGoal, Mb6.socGoal, Mb7.socGoal)
socGoal <- socGoal0 %>%
  mutate(condition = paste(utterance, emotion),
         condition = factor(condition, levels = c("good smile", "bad frown", "good frown", "bad smile")))
  
pd <- position_dodge(0.2)
socGoal.plot <- ggplot(socGoal, aes(x = socGoal, y = expval, 
                                group = condition,
                                color=condition)) +
  geom_line(position=pd) +
  geom_point(position=pd) +
  scale_color_brewer(palette="Dark2") +
  theme_bw() +
  theme(legend.position='none')+
  ylim(0, 0.3) +
  #xlab("social goal") +
  scale_x_continuous(name="social goal", breaks = c(0, 0.4, 0.8)) +
  ylab("posterior probability mass") +
  #ggtitle("\"How likely do you think the speaker's goal was to be nice?\"") +
  theme(legend.position='none',
        plot.title = element_text(hjust = 0.5)) +
  facet_grid(cols = vars(model))
socGoal.plot
```
###infGoal & socGoal: human
```{r}
dGoal.raw <- read.csv(here("models/201221EMO-RSA_MAIN_COMMGOALS_PREREGISTERED_DONOTCHANGE_January 13, 2021_20.41.csv"))
dGoal <- dGoal.raw %>%
  slice(-1:-2) %>%
  filter(Q358 != "", Q129 != "test") %>%
  select(ResponseId, starts_with("PUtt_"), starts_with("NUtt_")) %>%
  pivot_longer(cols = c(starts_with("PUtt_"), starts_with("NUtt_")), 
               names_to = "trial", values_to = "response") %>%
  separate(trial, into=c("utt","exp","race", "gender","question", "random")) %>%
  rename(id = `ResponseId`) %>%
  mutate(question = case_when(question == "feed" ~ "informational goal",
                              question == "nice" ~ "social goal",
                              question == "check" ~ "check"),
         condition = case_when(utt == "PUtt" & exp == "PExp" ~ "PU_PE",
                               utt == "PUtt" & exp == "NExp" ~ "PU_NE",
                               utt == "NUtt" & exp == "PExp" ~ "NU_PE",
                               utt == "NUtt" & exp == "NExp" ~ "NU_NE"),
         condition = fct_relevel(condition, "PU_PE", "PU_NE", "NU_PE", "NU_NE"),
         response = fct_relevel(response, "1", "2", "3", "4")) %>%
  select(-random) %>%
  filter(response != "") 

checksGoal <- dGoal %>%
  filter(question == "check") %>%
  mutate(check_score = case_when(race == "A" & grepl("H", response, ignore.case = TRUE) ~ 1,
                                 race == "B" & grepl("O", response, ignore.case = TRUE) ~ 1,
                                 race == "L" & grepl("U", response, ignore.case = TRUE) ~ 1,
                                 race == "W" & grepl("L", response, ignore.case = TRUE) ~ 1,
                                 TRUE ~ 0)) %>%
  group_by(id) %>%
  summarize(perc_correct = mean(check_score))

ggplot(checksGoal, aes(perc_correct)) +
  geom_histogram(binwidth=.01) +
  theme_bw() +
  xlab("accuracy on check questions") +
  ylab("number of participants")

# Only include those who got all check questions correct
dGoal <- full_join(dGoal, checksGoal) %>%
  filter(perc_correct == 1) %>%
  filter

dGoal2 <- dGoal %>%
  mutate(utt = case_when(utt == "PUtt" ~ "good",
                         utt == "NUtt" ~ "bad"),
         exp = case_when(exp == "PExp" ~ "smile",
                         exp == "NExp" ~ "frown"),
         utt = fct_relevel(utt, "good"),
         exp = fct_relevel(exp, "smile"),
         condition = case_when(condition=="PU_PE" ~ "good smile",
                               condition=="NU_NE" ~ "bad frown",
                               condition=="PU_NE" ~ "good frown",
                               condition=="NU_PE" ~ "bad smile"),
         condition = factor(condition, levels=c("good smile", "bad frown", "good frown", "bad smile"))) %>%
  filter(question!="check") %>%
  select(-perc_correct)

#write.csv(dGoal2, here("models/clean_data_goals.csv"), row.names = FALSE)

# infGoal: human
dInf <- dGoal2[dGoal2$question=="informational goal",]
n_conditionInf <- dInf %>%
  group_by(condition) %>%
  count() 
n_conditionInf
d.infGoal <- dInf %>%
  group_by(condition, response) %>%
  count() %>%
  mutate(proportion = case_when(condition=="good smile" ~ n/58,
                           condition=="good frown" ~ n/59,
                           condition=="bad smile" ~ n/58,
                           condition=="bad frown" ~ n/60),
         ci_l = case_when(condition=="good smile" ~ prop.test(n, 58)$conf.int[1],
                           condition=="good frown" ~ prop.test(n, 59)$conf.int[1],
                           condition=="bad smile" ~ prop.test(n, 58)$conf.int[1],
                           condition=="bad frown" ~ prop.test(n, 60)$conf.int[1]),
         ci_u = case_when(condition=="good smile" ~ prop.test(n, 58)$conf.int[2],
                           condition=="good frown" ~ prop.test(n, 59)$conf.int[2],
                           condition=="bad smile" ~ prop.test(n, 58)$conf.int[2],
                           condition=="bad frown" ~ prop.test(n, 60)$conf.int[2]))  
h.infGoal.plot <- d.infGoal %>%
  ggplot(., aes(x = response, y = proportion, group = condition, color=condition))+
  geom_line(position=pd) +
  geom_point(position=pd) +
  geom_pointrange(aes(ymin=ci_l, ymax=ci_u), size=0.25, position=pd) +
  scale_color_brewer(palette="Dark2") +
  ylim(0, 1) +
  xlab("informational goal") +
  ylab("proportion chosen") +
  theme_bw() + 
  #ggtitle("Human Data") +
  theme(plot.title = element_text(hjust = 0.5))
h.infGoal.plot

# socGoal: human
dSoc <- dGoal2[dGoal2$question=="social goal",]
n_conditionSoc <- dSoc %>%
  group_by(condition) %>%
  count() 
n_conditionSoc

d.socGoal <- dSoc %>%
  group_by(condition, response) %>%
  count() %>%
  mutate(proportion = case_when(condition=="good smile" ~ n/58,
                           condition=="good frown" ~ n/58,
                           condition=="bad smile" ~ n/58,
                           condition=="bad frown" ~ n/59),
         ci_l = case_when(condition=="good smile" ~ prop.test(n, 58)$conf.int[1],
                           condition=="good frown" ~ prop.test(n, 58)$conf.int[1],
                           condition=="bad smile" ~ prop.test(n, 58)$conf.int[1],
                           condition=="bad frown" ~ prop.test(n, 59)$conf.int[1]),
         ci_u = case_when(condition=="good smile" ~ prop.test(n, 58)$conf.int[2],
                           condition=="good frown" ~ prop.test(n, 58)$conf.int[2],
                           condition=="bad smile" ~ prop.test(n, 58)$conf.int[2],
                           condition=="bad frown" ~ prop.test(n, 59)$conf.int[2]))  

h.socGoal.plot <- d.socGoal %>%
  ggplot(., aes(x = response, y = proportion, group = condition, color=condition))+
  geom_line(position=pd) +
  geom_point(position=pd) +
  geom_pointrange(aes(ymin=ci_l, ymax=ci_u), size = 0.25, position=pd) +
  scale_color_brewer(palette="Dark2") +
  ylim(0, 1) +
  xlab("social goal") +
  ylab("proportion chosen") +
  theme_bw() + 
  #ggtitle("Human Data") +
  theme(plot.title = element_text(hjust = 0.5))
h.socGoal.plot
```

###infGoal: total
```{r}
infGoal.total <- infGoal.plot + h.infGoal.plot + plot_layout(ncol=2, widths=c(16,0.9))
infGoal.total
```
###socGoal: total
```{r}
socGoal.total <- socGoal.plot + h.socGoal.plot + plot_layout(ncol=2, widths=c(16, 0.9))
socGoal.total
```
###total
```{r}
total <- state.total / infGoal.total / socGoal.total
ggsave(here("models/plots_16models_graded.pdf"), width=22, height=8)

# without human data
# total <- state.plot + infGoal.plot + socGoal.plot & theme(legend.position = "right") 
# total + plot_layout(ncol=1, guides = "collect")
# ggsave(here("models/plots_16models_graded_predictions.pdf"), width=24, height=8)
```

# ## line plots - averaged
# ### state
# ```{r}
# model_state_ave <- state %>%
#   mutate(score = state*expval) %>%
#   group_by(model, condition) %>%
#   summarise(mean = mean(score)) 
# human.state.ave <- d.state %>%
#   mutate(score = (as.numeric(response)-1) * probability /7) %>%
#   group_by(condition) %>%
#   summarise(mean=sum(score)) %>%
#   mutate(model = "pilot data")
# state_ave <- rbind(data.frame(model_state_ave), data.frame(human.state.ave))
# #state_ave$model <- factor(state_ave$model, levels = c("M: UttInfNoEmo","M0: NoEmo", "M1: EmoComm", "M1a1: UttInfEmoSoc","M1a3: EmoSoc", "M2: EmoNotComm", "M3: InferEmoComm", "M3a: InferEmoTrue/Soc",  "human (pilot)"))  
# 
# state_ave_plot <- ggplot(state_ave, aes(x = model, y = mean, 
#                                 group = condition, color=condition))+
#   geom_line(position=pd) +
#   geom_point(position=pd) +
#   scale_color_brewer(palette="Dark2") +
#   ylim(0, 1) +
#   xlab("state") +
#   theme_bw() + 
#   #ggtitle("Human") +
#   theme(plot.title = element_text(hjust = 0.5))
# state_ave_plot
# ```
# ### infGoal
# ```{r}
# model_infGoal_ave <- infGoal %>%
#   mutate(score = infGoal*expval) %>%
#   group_by(model, condition) %>%
#   summarise(mean = sum(score)) 
# human.infGoal.ave <- d.infGoal %>%
#   mutate(score = (as.numeric(response)-1) * probability /7) %>%
#   group_by(condition) %>%
#   summarise(mean=sum(score)) %>%
#   mutate(model = "pilot data")
# infGoal_ave <- rbind(data.frame(model_infGoal_ave), data.frame(human.infGoal.ave))
# #infGoal_ave$model <- factor(infGoal_ave$model, levels = c("M: UttInfNoEmo","M0: NoEmo", "M1: EmoComm","M1a1: UttInfEmoSoc", "M1a3: EmoSoc", "M2: EmoNotComm", "M3: InferEmoComm", "M3a: InferEmoTrue/Soc",  "human (pilot)"))  
# 
# infGoal_ave_plot <- ggplot(infGoal_ave, aes(x = model, y = mean, 
#                                 group = condition, color=condition))+
#   geom_line(position=pd) +
#   geom_point(position=pd) +
#   scale_color_brewer(palette="Dark2") +
#   ylim(0, 1) +
#   xlab("infGoal") +
#   theme_bw() + 
#   #ggtitle("Human") +
#   theme(plot.title = element_text(hjust = 0.5))
# infGoal_ave_plot
# ```
# ### socGoal
# ```{r}
# model_socGoal_ave <- socGoal %>%
#   mutate(score = socGoal*expval) %>%
#   group_by(model, condition) %>%
#   summarise(mean = sum(score)) 
# human.socGoal.ave <- d.socGoal %>%
#   mutate(score = (as.numeric(response)-1) * probability /7) %>%
#   group_by(condition) %>%
#   summarise(mean=sum(score)) %>%
#   mutate(model = "pilot data")
# socGoal_ave <- rbind(data.frame(model_socGoal_ave), data.frame(human.socGoal.ave))
# #socGoal_ave$model <- factor(socGoal_ave$model, levels = c("M: UttInfNoEmo", "M0: NoEmo", "M1: EmoComm","M1a1: UttInfEmoSoc","M1a3: EmoSoc", "M2: EmoNotComm", "M3: InferEmoComm", "M3a: InferEmoTrue/Soc",  "human (pilot)"))  
# 
# socGoal_ave_plot <- ggplot(socGoal_ave, aes(x = model, y = mean, 
#                                 group = condition, color=condition))+
#   geom_line(position=pd) +
#   geom_point(position=pd) +
#   scale_color_brewer(palette="Dark2") +
#   ylim(0, 1) +
#   xlab("socGoal") +
#   theme_bw() + 
#   #ggtitle("Human") +
#   theme(plot.title = element_text(hjust = 0.5))
# socGoal_ave_plot
# ```
# ### inferEmoComm
# ```{r}
# Ma5_emoComm_ave <- Ma5.emoComm %>%
#   mutate(condition = paste(utterance, emotion),
#          emoComm = case_when(emoComm=="FALSE" ~ 0,
#                              emoComm=="TRUE" ~ 1),
#          score = emoComm * expval) %>%
#   group_by(condition, model) %>%
#   summarise(mean=sum(score))
# Ma6_emoComm_ave <- Ma6.emoComm %>%
#   mutate(condition = paste(utterance, emotion),
#          emoComm = case_when(emoComm=="FALSE" ~ 0,
#                              emoComm=="TRUE" ~ 1),
#          score = emoComm * expval) %>%
#   group_by(condition, model) %>%
#   summarise(mean=sum(score))
# 
# Ma7_emoComm_ave <- Ma7.emoComm %>%
#   mutate(condition = paste(utterance, emotion),
#          emoComm = case_when(emoComm=="FALSE" ~ 0,
#                              emoComm=="TRUE" ~ 1),
#          score = emoComm * expval) %>%
#   group_by(condition, model) %>%
#   summarise(mean=sum(score))
# 
# Mb5_emoComm_ave <- Mb5.emoComm %>%
#   mutate(condition = paste(utterance, emotion),
#          emoComm = case_when(emoComm=="FALSE" ~ 0,
#                              emoComm=="TRUE" ~ 1),
#          score = emoComm * expval) %>%
#   group_by(condition, model) %>%
#   summarise(mean=sum(score))
# Mb6_emoComm_ave <- Mb6.emoComm %>%
#   mutate(condition = paste(utterance, emotion),
#          emoComm = case_when(emoComm=="FALSE" ~ 0,
#                              emoComm=="TRUE" ~ 1),
#          score = emoComm * expval) %>%
#   group_by(condition, model) %>%
#   summarise(mean=sum(score))
# 
# Mb7_emoComm_ave <- Mb7.emoComm %>%
#   mutate(condition = paste(utterance, emotion),
#          emoComm = case_when(emoComm=="FALSE" ~ 0,
#                              emoComm=="TRUE" ~ 1),
#          score = emoComm * expval) %>%
#   group_by(condition, model) %>%
#   summarise(mean=sum(score))
# 
# Ma0_emoComm_ave <- Ma5_emoComm_ave %>%
#   mutate(model= "Ma0: UttInfEmoNon", mean = NA)
# Ma1_emoComm_ave <- Ma5_emoComm_ave %>%
#   mutate(model= "Ma1: UttInfEmoSoc", mean = NA)
# Ma2_emoComm_ave <- Ma5_emoComm_ave %>%
#   mutate(model= "Ma2: UttInfEmoBal", mean = NA)
# Ma3_emoComm_ave <- Ma5_emoComm_ave %>%
#   mutate(model= "Ma3: UttInfEmoTru", mean = NA)
# Ma4_emoComm_ave <- Ma5_emoComm_ave %>%
#   mutate(model= "Ma4: UttInfEmoInf", mean = NA)
# Mb0_emoComm_ave <- Ma5_emoComm_ave %>%
#   mutate(model= "Mb0: UttBalEmoNon", mean = NA)
# Mb1_emoComm_ave <- Ma5_emoComm_ave %>%
#   mutate(model= "Mb1: UttBalEmoSoc", mean = NA)
# Mb2_emoComm_ave <- Ma5_emoComm_ave %>%
#   mutate(model= "Mb2: UttBalEmoBal", mean = NA)
# Mb3_emoComm_ave <- Ma5_emoComm_ave %>%
#   mutate(model= "Mb3: UttBalEmoTru", mean = NA)
# Mb4_emoComm_ave <- Ma5_emoComm_ave %>%
#   mutate(model= "Mb4: UttBalEmoInf", mean = NA)
# h_emoComm_ave <- Ma5_emoComm_ave %>%
#   mutate(model= "pilot data", mean = NA)
# emoComm_ave <- rbind(Ma0_emoComm_ave,Ma1_emoComm_ave, Ma2_emoComm_ave, Ma3_emoComm_ave, 
#                      Ma4_emoComm_ave, Ma5_emoComm_ave, Ma6_emoComm_ave, Ma7_emoComm_ave, 
#                      Mb0_emoComm_ave,Mb1_emoComm_ave, Mb2_emoComm_ave, Mb3_emoComm_ave, 
#                      Mb4_emoComm_ave, Mb5_emoComm_ave, Mb6_emoComm_ave, Mb7_emoComm_ave, h_emoComm_ave)
# emoComm_ave <- emoComm_ave %>%
#   mutate(condition = factor(condition, levels = c("good smile", "bad frown", "good frown", "bad smile")))
# 
# emoComm_ave_plot <- ggplot(emoComm_ave, aes(x = model, y = mean, 
#                                 group = condition, color=condition))+
#   geom_line(position=pd) +
#   geom_point(position=pd) +
#   scale_color_brewer(palette="Dark2") +
#   ylim(0, 1) +
#   xlab("emoComm") +
#   theme_bw() + 
#   #ggtitle("Human") +
#   theme(plot.title = element_text(hjust = 0.5))
# emoComm_ave_plot
# ggsave(here("models/plots_emocomm.pdf"), width=25, height=3)
# 
# ```
# ###total
# ```{r}
# #total_ave <- state_ave_plot + infGoal_ave_plot + socGoal_ave_plot + emoComm_ave_plot & theme(legend.position = "top") 
# total_ave <- state_ave_plot + infGoal_ave_plot + socGoal_ave_plot & theme(legend.position = "top") 
# total_ave + plot_layout(ncol=1, guides = "collect")
# ggsave(here("models/plots_14models_averaged.pdf"), width=22, height=8)
# ```
# 
# ### analysis
# ```{r cache = TRUE}
# d2$response <- as.numeric(d2$response)
# # Bayesian mixed-effects model
# state <- brm(response ~ utt * exp + (1 + utt*exp|id) + (1 + utt*exp|race), 
#              data = d2[d$question=="ground truth",], 
#              family = cumulative(link = "logit", threshold = "flexible"))
# summary(state)
# infGoal <- brm(response ~ utt * exp + (1 + utt*exp|id) + (1 + utt*exp|race), 
#                data = d2[d$question=="accurate feedback",],
#                family = cumulative(link = "logit", threshold = "flexible"))
# summary(infGoal)
# socGoal <- brm(response ~ utt * exp + (1 + utt*exp|id) + (1 + utt*exp|race),
#                data = d2[d$question=="niceness",],
#                family = cumulative(link = "logit", threshold = "flexible"))
# summary(socGoal)
# 
# # socGoal <- brm(response ~ condition + (1 + condition|id) + (1 + condition|race),
# #                data = d2[d$question=="niceness",],
# #                family = cumulative(link = "logit", threshold = "flexible"))
# # summary(socGoal)
# 
# # linear mixed-effects model
# state <- lmer(response ~ utt * exp + (1|id), data = d2[d$question=="ground truth",])
# summary(state)
# infGoal <- lmer(response ~ utt * exp + (1|id), data = d2[d$question=="accurate feedback",])
# summary(infGoal)
# socGoal <- lmer(response ~ utt * exp + (1|id), data = d2[d$question=="niceness",])
# summary(socGoal)
# ```
